ShrinkNets: Learning Network Size while Training

### 2018-05-17 paper/NIPS/evaluation.tex
Pass on Related Work + Add imageNet

\begin{figure}[htb]
\begin{center}
\vspace{-.1in}
\includegraphics[width=1\columnwidth]{size_evolution}
\vspace*{-5mm} 
\caption{ Evolution of the size of
  each layer over time (lighter: beginning, darker: end). On top a very large
  network performing $92.07\%$, at the bottom a simpler model with $90.5\%$
  accuracy. 
} 
\label{fig:network_size_evolution}
\end{center}
\vspace*{-4mm}
\end{figure}

@@

To illustrate this point on a larger dataset, we show two examples of
architectures learned by \shrink in
Figure~\ref{fig:network_size_evolution}.  The right arrow shows the model with the
best test accuracy, with identical performance to the best static
network; the left arrow shows a network that slightly under-performs the best in
terms of accuracy but is significantly smaller that the best equivalent
\textit{Static Network}.  In the plot, the dashed line
shows the number of neurons in each layer of the original VGG net, and the
shaded regions show the size of the \shrink as it converges (with the darkest
region representing the fully converged network).  Observe that the final
network that is trained looks quite different in the two cases, with the optimal
performing network appearing similar to the original VGG net, whereas the
shrunken network allocates many fewer neurons to the middle layers, and then
additional neurons to the final fewer layers.

>>>>

\begin{figure}[htb]
\begin{center}
\vspace{-.1in}
\includegraphics[width=1\columnwidth]{size_evolution}
\vspace*{-5mm} 
\caption{ Evolution of the size of
  each layer over time (lighter: beginning, darker: end). On the left a VGG
  network on \texttt{CIFAR10} with $90.5\%$ accuracy. On the right, ResNet-50
  on \texttt{ImageNet} that yields a top-1 accuracy of $71.57\%$.
} 
\label{fig:network_size_evolution}
\end{center}
\vspace*{-4mm}
\end{figure}

@@

To illustrate this point on a larger dataset, we show two examples of
architectures learned by \shrink. The first one is directly taken from
Figure~\ref{fig:network_size_evolution} and is typically a good trade-of between
size and accuracy. The right one is the evolution the ResNet-50 model
\cite{He2016a} trained on the ImageNet. In the plot, the dashed line
shows the number of neurons in each layer of the original architecture, and the
shaded regions show the size of the \shrink as it converges (with the darkest
region representing the fully converged network).  Observe that the final
network that is trained looks quite different in the two cases, with the optimal
performing network appearing similar to the original VGG net, whereas the
shrunken network allocates many fewer neurons to the middle layers, and then
additional neurons to the final fewer layers.

### 2018-05-17 paper/NIPS/related_work.tex
Pass on Related Work + Add imageNet

\noindent\textbf{Hyperparameter optimization techniques: }
One way to optimize network architecture is to use 
hyperparameter optimization. Although many methods have been 
proposed for hyperparameter optimization, simple techniques such as randomized
search have been shown to work suprisingly well in practice~\cite{BergstraJAMESBERGSTRA2012,Snoek12}.
%  Brute force search of network sizes is
%also become more practical due to faster and more powerful
%hardware~\cite{molchanov2016pruning}.  
The more complex methods include Bayesian techniques such as~\cite{Snoek12} that
select hyperparameter combinations from uncertain areas of the
hyperparameter space. 
Recently, methods based on bandit algorithms (e.g.
~\cite{li2016hyperband, jamieson2016}) have also been proposed to tune
hyperparameters by quickly discarding 
model configurations that perform badly. 
Although these methods can be used to tune the size of each layer in a network, 
in practice, related work presents limited experimental evidence
regarding this, likely because treating each layer as a hyperparameter
would lead to an excessively large search space.
In contrast, with \shrink, the size of the network can be tuned with 
a single parameter.
% More importantly, none of the hyperparameter optimization methods focuses on
% finding small networks, which is a crucial property of ShrinkNets, necessary to
% achieve good inference times.

@@

\noindent\textbf{Dynamically Sizing Networks: }The techniques closest to our
proposed method are those based on group sparsity such as
~\cite{Scardapane2017}, and those like~\cite{Philipp} that dynamically grow and shrink
 the size of the network during training.  \cite{Scardapane2017}
presents a method that also deactivates neurons using a loss function based on
group-sparsity.  However, the exact details of how their method works are not
given, and their experimental results (on a small, fully connected network), are
substantially worse than ours as shown in Section 5.
\cite{Philipp} propose a method called Adaptive Radial-Angular Gradient Descent
that adds neurons on the fly and removes neurons via an $l_2$ penalty.  However,
this approach requires a new optimizer and takes longer to converge compared to
ShrinkNets.

>>>>

\noindent\textbf{Hyperparameter optimization techniques: }
One way to optimize network architecture is to use 
hyperparameter optimization. Although many methods have been 
proposed for hyperparameter optimization, simple techniques such as randomized
search have been shown to work suprisingly well in practice~\cite{BergstraJAMESBERGSTRA2012,Snoek12}.
%  Brute force search of network sizes is
%also become more practical due to faster and more powerful
%hardware~\cite{molchanov2016pruning}.  
The more complex methods include Bayesian techniques such as~\cite{Snoek12} that
select hyperparameter combinations from uncertain areas of the
hyperparameter space. 
Recently, methods based on bandit algorithms (e.g.
~\cite{li2016hyperband, jamieson2016}) have also been proposed to tune
hyperparameters by quickly discarding 
model configurations that perform badly. 
Although these methods can be used to tune the size of each layer in a network, 
in practice, related work presents limited experimental evidence
regarding this, likely because treating each layer as a hyperparameter
would lead to an excessively large search space.
In contrast, with \shrink, the size of the network can be tuned with 
a single parameter. Recently, methods based on reinforcement learning have been
proposed (\cite{Zoph2017b,Zoph2017a}) and shown to generate very accurate
networks (NAS-Net). However as stated in \cite{Zoph2017b}, they still used the popular
heuristic that doubles the number of channels every time the dimension of
features is reduced without challenging it.

\gl{Add another paragraph on architectures that are small by design ? (MobileNet
ShuffleNet)}

% More importantly, none of the hyperparameter optimization methods focuses on
% finding small networks, which is a crucial property of ShrinkNets, necessary to
% achieve good inference times.

@@

\paragraph{Dynamically Sizing Networks}The techniques closest to our
proposed method are those based on group sparsity such as
~\cite{Scardapane2017,Alvarez2016a}, nuclear norm \cite{Alvarez2017a} and even
physics-inspired methods \cite{Wen2017}. In \cite{Wen2016}, authors look beyond
removing channels and experiment with shape and depth. In ~\cite{Philipp},
network is dynamically grown and shrunk during training.  \cite{Scardapane2017}
presents a method that also deactivates neurons using a loss function based on
group-sparsity.  However, the exact details of how their method works are not
given, and their experimental results (on a small, fully connected network), are
substantially worse than ours as shown in Section 5.  \cite{Philipp} propose a
method called Adaptive Radial-Angular Gradient Descent that adds neurons on the
fly and removes neurons via an $l_2$ penalty.  However, this approach requires a
new optimizer and takes longer to converge compared to \shrink.
\cite{Liu} is similar with \shrink in a sense that they both scale each
channel/neuron by a scalar, however our approach is more general since it can be
used with any architecture, even if they do not use batch normalization
\gl{say that they don't do neural garbage collection ?}.
